Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-06-14 mu/article/article.tex
Conclusions and article almost completed before BMS review

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
                        % documents and URLs 
\usepackage{blindtext}  % fill text
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
\usepackage{showframe}
\usepackage[inline]{showlabels}

@@

Using those structures we address a theoretical study of the spin velocity
injection (SVI) by one-photon absorption of linearly polarized light making
emphasis for the particular cases when the spin of electrons is directed along
the the $z$ Cartesian coordinate, perpendicular to the $xy$ plane of the
structure, or for the case when the velocity is directed along the $x$ and $y$
Cartesian direction on the $xy$ plane of the structures.
% 
The SVI ($\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$) is a nonlinear optical
effect that quantifies the velocity at which a PSC moves along the Cartesian
direction $\mathrm{b}$ with the spin of electron polarized along the Cartesian
direction $\mathrm{a}$. One photon absorption of linearly polarized light can
promote a distribution of electrons in $\mathbf{k}$ space regardless the
symmetry of the material resulting in a not net electrical
current. Then, the electrons excited to the conduction bands at
opposite $\mathbf{k}$ points will result in opposite spin polarizations 
producing no net spin injection.\cite{bhatPRL05} If the crystalline structure of
the material is not centrosymmetric the spin polarization injected at a given $
\mathbf{k}$ point could not vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and
then a PSC will be produced since the velocities of electrons at opposite
$\mathbf{k}$ points are opposite.

@@

We define the SVI as the velocity at which the spin, polarized along the
direction $\mathrm{a}$, propagates along the direction $\mathrm{b}$ as
\begin{equation}\label{eq:vab-w}
\mathcal{V}^{\mathrm{ab}}(\omega) \equiv
\frac{\dot{K}^{\mathrm{ab}}(\omega)}{(\hbar/2) \dot{n}(\omega)},
\end{equation}  
where the pure spin density injection current, $\dot{K}^{\mathrm{ab}} (\omega)$,
and the carrier injection rate, $\dot{n}(\omega)$, are given by
% 
\begin{equation}\label{eq:dot-kn}
\begin{aligned}
\dot{K}^{\mathrm{ab}}(\omega) 
&=
\mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega),
% \label{eq:dotk} 
\\
\dot{n}(\omega)
&=
\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega),
% \label{eq:dotn}
\end{aligned}
\end{equation}
where the roman superscripts denote Cartesian directions, and if repeated, they
are to be summed over, the $\xi^{\mathrm{ab}}(\omega)$ are the carrier
generation rate tensor components and $\mu^{\mathrm{abcd}}(\omega)$ are the pure
spin-current pseudotensor components given by\cite{bhatPRL05}
\begin{equation*}\label{eq:mu}
\begin{aligned}
\mu^{\mathrm{abcd}}  (\omega) &
=
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}} \times \\
\sum_{vcc'}^{'}
\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'} 
\left( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
(c \leftrightarrow d)
\right) 
\right] \delta(\omega-\omega_{cv}),
\end{aligned}
\end{equation*}
where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
\sum_{\ell}v^{\mathrm{a}}_{nl}(\mathbf{k}) S^{\mathrm{b}}_{lm}(\mathbf{k})$ are
the spin current matrix elements that, using time reversal invariance, satisfy
the relation $K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k})
$. 
% 
The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and the
sum only covers these states and since $\mu^{\mathrm{abcd}}(\omega)$ is real we
have that $\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.
% 
Since we have 2D structures we use an incoming electric field parallel to the
surface, $\mathbf{E}^{a}(\omega) = E^{\mathrm{a}} e^{i(\alpha + \omega t)}$,
where the angle $\alpha$ corresponds to the linear polarization angle measured
positively in the counter-clockwise from the $x$ direction on the
surface of the structures.
% 
Then from Eq. \eqref{eq:dot-kn} we can rewrite the Eq. \eqref{eq:vab-w} and 
including the polarization angle dependence we have
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)},
\label{eq:vab-aw}
\end{align}
\end{widetext}
% 
If the polarization angle is fixed to $\alpha = \frac{\pi}{4}$ the previous
expression can be reduced to 
\begin{equation*}\label{eq:vab-90deg}
\mathcal{V}^{\mathrm{ab}} (\omega)
= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\end{equation*}
Two interesting possibilities to analyze the SVI are fixing the spin along any
of the three Cartesian coordinates and, for our cases, particularly for the spin
directed along $z$ directed perpendicularly to the surface of the structure; or
fixing the velocity along the $x$ or $y$ Cartesian coordinates on the $xy$ plane
of the structures. In following subsections we present these cases.

@@

Because we have 2D structures, one of the options to analyze the spin velocity
(Eq. \eqref{eq:vab-aw}) is fixing the spin parallel to the surface of the
structure in the $x$ or $y$ directions or perpendicularly to it in the $z$
direction. We define the magnitude of the spin velocity with spin polarization
along the $\mathrm{b}$ Cartesian coordinate as
\begin{equation}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
=
\sqrt{
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\end{equation}
and the angle at which the spin velocity is directed on the $xy$ plane as
\begin{equation}
\gamma_{\mathrm{b}} (\omega,\alpha)
=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\label{eq:gamma-ang}
\end{equation}
where the angle is measured in the counter-clockwise direction from the
positive $x$ Cartesian coordinate. {\color{red} We also define two special
angles
\begin{align}
\gamma_{\mathrm{b \parallel}}(\omega,\alpha) &= \alpha, 
\label{eq:gamma-par} 
\\
\gamma_{\mathrm{b \perp}}(\omega,\alpha) &= \alpha \pm 90^{\circ}.
\label{eq:gamma-perp}
\end{align}
The first corresponds to the case when the spin velocity is directed, on the
$xy$ plane in the same direction of the polarization angle of the incoming
beam; the second one corresponds to the case when the spin velocity is directed
perpendicularly respect to the polarization angle of the incoming beam. }

@@

{\color{red} Another possibility to analyze the Eq. \eqref{eq:vab-aw} is fixing
the velocity on the $xy$ plane along $x$ or $y$ Cartesian coordinate and then
define the magnitude of the spin velocity directed along the $\mathrm{a}$
direction as}
\begin{align}
|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
},
\label{eq:vv-mag}
\end{align}
{\color{red} Then, the spin direction depends of the $x$, $y$, and $z$
components of the previous equation and so we define the spin orientation polar
and azimuthal angles as}
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}
{\color{red} where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the
positive to the negative $z$ Cartesian coordinate and
$\varphi_{\mathrm{a}}(\omega,\alpha)$ is measured on the $xy$ plane in the
counter-clockwise direction from the positive $x$ Cartesian coordinate.}

@@

For a layered system we have that the total contribution of Eqns. 
\eqref{eq:vs-mag} and \eqref{eq:vv-mag} is given \cite{arzatePRB14} by

\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|
=& 
\ell_{\mathrm{eff}}
\sum_{\ell=1}^{N_{\mathrm{eff}}}
|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega,\alpha)|
\label{eq:vs-layer}
\\
|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|
=&
\ell_{\mathrm{eff}}
\sum_{\ell=1}^{N_{\mathrm{eff}}}
|\mathcal{V}^{\mathrm{a}} (\ell | \omega,\alpha)|
\label{eq:vv-layer}
\end{align}

@@

In Fig. \ref{fig:alt-3d-vsb} we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained for the \emph{alt} structure .
% From this figure we found that the zone where the absolute maximum response
% is held corresponds to a energy range from 0.90\,eV to 0.93\,eV and
% polarization angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a
% local maximum is obtained for the same polarization angles but for energies
% between 0.67\,eV and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
% 
{\color{red} From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have
that the absolute maximum response is obtained for an incoming beam with
polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane.
% 
Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
velocity angle is centered at $51.5^{\circ}$ having variations of $\pm
2^{\circ}$ for the polarization angle range $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
As made in the previous analysis the circled box indicates the collinear angle
(Eq. \eqref{eq:gamma-par}) $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
53.5^{\circ}$ corresponding a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the blue
square box indicates the perpendicular angles corresponding values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.}
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented
here. The absolute maxima for the cases when the spin polarization are directed
in the $\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of
the incoming beam equal to 0.912\,eV and polarization angle
$\alpha=145^{\circ}$ resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.

@@

>>>>

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
                        % documents and URLs 
\usepackage{blindtext}  % fill text
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
% \usepackage{showframe}
% \usepackage[inline]{showlabels}

@@

Using those structures we address a theoretical study of the spin velocity
injection (SVI) by one-photon absorption of linearly polarized light that does
not seem to have been reported previously.
% 
We calculated the responses for the particular cases when the spin of electrons
is directed along the the $z$ Cartesian coordinate, perpendicular to the $xy$
plane of the structure, or for the case when the velocity is directed along the
$x$ and $y$ Cartesian direction on the $xy$ plane of the structures.
% 
The SVI ($\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$) is optical effect that
quantifies the velocity at which a PSC moves along the Cartesian direction
$\mathrm{b}$ with the spin of electron polarized along the Cartesian direction
$\mathrm{a}$. One photon absorption of linearly polarized light can promote a
distribution of electrons in $\mathbf{k}$ space regardless the symmetry of the
material resulting in a not net electrical current. Then, the electrons excited
to the conduction bands at opposite $\mathbf{k}$ points will result in opposite
spin polarizations producing no net spin injection.\cite{bhatPRL05} If the
crystalline structure of the material is not centrosymmetric the spin
polarization injected at a given $\mathbf{k}$ point could not
vanish\cite{alvaradoPRL85, schmiedeskampPRL88} and then a PSC will be produced
since the velocities of electrons at opposite $\mathbf{k}$ points are opposite.

@@

We define the SVI as the velocity at which the spin, polarized along the
direction $\mathrm{a}$, propagates along the direction $\mathrm{b}$ as
\begin{equation}\label{eq:vab-w}
\mathcal{V}^{\mathrm{ab}}(\omega) \equiv
\frac{\dot{K}^{\mathrm{ab}}(\omega)}{(\hbar/2) \dot{n}(\omega)},
\end{equation}  
where the pure spin density injection current, $\dot{K}^{\mathrm{ab}}
(\omega)$, and the carrier injection rate, $\dot{n}(\omega)$, are given by
% 
\begin{equation}\label{eq:dot-kn}
\begin{aligned}
\dot{K}^{\mathrm{ab}}(\omega) 
&=
\mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega),
% \label{eq:dotk} 
\\
\dot{n}(\omega)
&=
\xi^{\mathrm{ab}}(\omega) E^{c }(\omega) E^{d*}(\omega),
% \label{eq:dotn}
\end{aligned}
\end{equation}
where the roman superscripts denote Cartesian directions, and if repeated, they
are to be summed over, the $\xi^{\mathrm{ab}}(\omega)$ are the carrier
generation rate tensor components and $\mu^{\mathrm{abcd}}(\omega)$ are the
pure spin-current pseudotensor components given by\cite{bhatPRL05}
\begin{equation*}\label{eq:mu}
\begin{aligned}
\mu^{\mathrm{abcd}}  (\omega) &
=
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}} \times \\
\sum_{vcc'}^{'}
\mathrm{Re} & \left[ K^{\mathrm{ab}}_{cc'} 
\left( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
(c \leftrightarrow d)
\right) 
\right] \delta(\omega-\omega_{cv}),
\end{aligned}
\end{equation*}
where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
\sum_{\ell}v^{\mathrm{a}}_{nl}(\mathbf{k}) S^{\mathrm{b}}_{lm}(\mathbf{k})$ are
the spin current matrix elements that, using time reversal invariance, satisfy
the relation $K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k})
$. 
% 
The $'$ in the sum means that $c$ and $c'$ are quasi degenerate states and the
sum only covers these states and since $\mu^{\mathrm{abcd}}(\omega)$ is real we
have that $\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.
% 
Since we have 2D structures we use an incoming electric field parallel to the
surface, $\mathbf{E}^{a}(\omega) = E^{\mathrm{a}} e^{i(\alpha + \omega t)}$,
where the angle $\alpha$ corresponds to the linear polarization angle measured
positively in the counter-clockwise from the $x$ direction on the
surface of the structures.
% 
Then from Eq. \eqref{eq:dot-kn} we can rewrite the Eq. \eqref{eq:vab-w} and 
including the polarization angle dependence we have
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)},
\label{eq:vab-aw}
\end{align}
\end{widetext}
% 
If the polarization angle is fixed to $\alpha = \frac{\pi}{4}$ the previous
expression can be reduced to 
\begin{equation*}\label{eq:vab-90deg}
\mathcal{V}^{\mathrm{ab}} (\omega)
= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\end{equation*}
Two interesting possibilities to analyze the SVI are fixing the spin along any
of the three Cartesian coordinates and, for our cases, particularly for the
spin directed along $z$ directed perpendicularly to the surface of the
structure; or fixing the velocity along the $x$ or $y$ Cartesian coordinates on
the $xy$ plane of the structures. Also we can analyze the SVI contribution
coming from each layer of the structure. In following subsections we present
these three cases.

@@

Analyzing the SVI, Eq. \eqref{eq:vab-aw}, we define the magnitude of the spin
velocity with spin polarized along the $\mathrm{b}$ Cartesian coordinate as
\begin{equation}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
=
\sqrt{
[\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\end{equation}
and the angle at which the spin velocity is directed on the $xy$ plane as
\begin{equation}
\gamma_{\mathrm{b}} (\omega,\alpha)
=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{yb}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{xb}}(\omega,\alpha)} \right),
\label{eq:gamma-ang}
\end{equation}
where this angle is measured in the counter-clockwise direction from the
positive $x$ Cartesian coordinate. We also define two special
angles
\begin{align}
\gamma_{\mathrm{b \parallel}}(\omega,\alpha) &= \alpha, 
\label{eq:gamma-par} 
\\
\gamma_{\mathrm{b \perp}}(\omega,\alpha) &= \alpha \pm 90^{\circ}.
\label{eq:gamma-perp}
\end{align}
The first corresponds to the case when the spin velocity is directed, on the
$xy$ plane in the same direction of the polarization angle $\alpha$ of the
incoming beam; the second one corresponds to the case when the spin velocity is
directed perpendicularly respect to the polarization angle of the incoming
beam.

@@

Analyzing now the SVI fixing the velocity along the $\mathrm{a}$ Cartesian
coordinate on the surface of the structures we define the corresponding
magnitude as
\begin{align}
|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
},
\label{eq:vv-mag}
\end{align}
{\color{red} Then, the spin direction depends of the $x$, $y$, and $z$
components of the previous equation and so we define the spin orientation polar
and azimuthal angles as}
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}
{\color{red} where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the
positive to the negative $z$ Cartesian coordinate and
$\varphi_{\mathrm{a}}(\omega,\alpha)$ is measured on the $xy$ plane in the
counter-clockwise direction from the positive $x$ Cartesian coordinate.}

@@

For a layered system we have that the total contribution of Eqns. 
\eqref{eq:vs-mag} and \eqref{eq:vv-mag} are given \cite{arzatePRB14} by 
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|
=& 
\ell_{\mathrm{eff}}
\sum_{\ell=1}^{N_{\mathrm{eff}}}
|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega,\alpha)|
\label{eq:vs-layer}
\\
|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|
=&
\ell_{\mathrm{eff}}
\sum_{\ell=1}^{N_{\mathrm{eff}}}
|\mathcal{V}^{\mathrm{a}} (\ell | \omega,\alpha)|
\label{eq:vv-layer}
\end{align}
where $|\mathcal{V}_{\sigma^{\mathrm{b}}} (\ell | \omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{a}} (\ell | \omega,\alpha)|$ gives the contribution of
the $\ell^{th}$ layer to the total SVI when the spin is fixed in the
$\mathrm{b}$ direction or when the velocity is fixed in the $\mathrm{a}$
direction, respectively. For the structures presented here this layers
correspond to the total number of layers being two for the \emph{up} structure
and six for the \emph{alt} structure.

@@

In Fig. \ref{fig:alt-3d-vsb} we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained for the \emph{alt} structure .
% From this figure we found that the zone where the absolute maximum response
% is held corresponds to a energy range from 0.90\,eV to 0.93\,eV and
% polarization angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a
% local maximum is obtained for the same polarization angles but for energies
% between 0.67\,eV and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
% 
{\color{red} From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have
that the absolute maximum response is obtained for an incoming beam with
polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane.
% 
Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
velocity angle is centered at $51.5^{\circ}$ having variations of $\pm
2^{\circ}$ for the polarization angle range $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
As made in the previous analysis the circled box indicates the collinear angle
(Eq. \eqref{eq:gamma-par}) $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
53.5^{\circ}$ corresponding a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the blue
square box indicates the perpendicular angles corresponding values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)|=43.0$\,Km/s.}
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented
here. The absolute maxima for the cases when the spin polarization are directed
in the $\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of
the incoming beam equal to 0.912\,eV and polarization angle
$\alpha=145^{\circ}$ resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.

@@

Spintronics devices are based on the control of spin and electrical charge
through electrical and optical methods.
% 
Semiconductor spintronics gives the development possibility of devices that can
perform high-volume information manipulation, processing, and storage, for
computing and communications technologies. \cite{awschalomNP2007}
% 
We have performed an \emph{ab initio} calculation for the SVI by one-photon
absorption of linearly polarized light in the \emph{up} and \emph{alt} 2D
hydrogenated graphene structures that could result in spintronics devices
development. This effect does not seem to have been reported previously.
% 
We calculated the responses for two cases: when the spin polarization is fixed
along the Cartesian coordinates and when the spin velocity is directed along
the $x$ and $y$ Cartesian directions on the $xy$ surface of the structures. We
found that  the SVI is very susceptible to the characteristics of the
structures presenting an anisotropic behavior.
% 
We found that for both structures it is possible to generate a SVI comparable
being the response of the \emph{alt} structure comparable with GaAs and CdSe
and the response of the \emph{up} structure much more intense than all.

We analyzed the SVI as a function of the energy of the incoming beam and the
polarization angle for the \emph{up} and \emph{alt} structures for the cases
when the spin is polarized along the three Cartesian directions with a
propagating angle on the surface of the structures measured in the counter-%
clockwise direction from the $x$ Cartesian direction. We found that the most
intense response was when the spin is directed perpendicularly to the plane of
the structures in the $z$ direction.
% 
For this condition we found that the \emph{up} structure reaches a maximum
$|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 95.8$\,Km/s directed in
an angle $\gamma_{\mathrm{z}} (\omega,\alpha) = 160^{\circ}$ on the $xy$ plane
for an energy of the incoming beam of 0.088\,eV, for which the response is
maximized, and polarization angle $\alpha
= 40^{\circ}$.
% 
Similarly for the \emph{alt} structure we found that the maximum reached is $|
\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| = 43.0$\,Km/s at $\gamma_{
\mathrm{z}} (\omega,\alpha) = 50^{\circ}$ for an energy of the incoming beam of
0.912\,eV and polarization angle $\alpha = 145^{\circ}$.
% 
Also we found two angles of interest for which the SVI, with spin polarized in
the $z$ direction, propagates collinearly or perpendicularly to the
polarization angle of the incoming beam. With this condition and fixing again
the energy of the incoming beam to 0.088\,eV we found that
$\gamma_{\mathrm{z}\parallel} (\omega,\alpha=65.5^{\circ}) = 65.5^{\circ}$
resulting in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)| =
82.3$\,Km/s and $\gamma_{\mathrm{z}\perp} (\omega,\alpha = 155.5^{\circ}) =
65.5^{\circ}$ resulting in a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)| = 24.8$\,Km/s.
% 
Alike, for the \emph{alt} structure fixing the energy of the incoming
beam to 0.912\,eV we found that the parallel and collinear angles are $\gamma_{
\mathrm{z}\parallel} (\omega,\alpha = 53.5^{\circ}) = 53.5^{\circ}$ and
$\gamma_{\mathrm{z}\perp} (\omega,\alpha = 140^{\circ}) = 50^{\circ}$ resulting
in values of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s
and $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s,
respectively.

We also examined the SVI for the cases when the velocity is directed along the
$x$ and $y$ Cartesian coordinates on the $xy$ plane of the \emph{up} and
\emph{alt} structures. We also defined the polar and azimuthal angles, the
first measured from the positive to the negative $z$ Cartesian coordinate
perpendicular to the structure and the second from the positive $x$ Cartesian
direction in the counter-clockwise sense on the $xy$ plane.
% 
For this case we found that the responses for the \emph{up} structure,for an
energy of the incoming bean of 0.088\,eV, reach the maximum values  of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=58.7$\,Km/s wit polar and azimuthal
% spin polarization angles $\theta_{\mathrm{x}} (\omega,\alpha)=47$ and
% $\varphi_{\mathrm{x}} (\omega,\alpha)=212$, 
directed upward the third Cartesian quadrant of the $xy$ plane; and
$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)|=87.9$\,Km/s with polar and
azimuthal spin polarization angles $\theta_{\mathrm{y}} (\omega,\alpha) =
8^{\circ}$ and $\varphi_{\mathrm{y}} (\omega,\alpha) = 133^{\circ}$ directed
almost perpendicularly over the first Cartesian quadrant over the $xy$ plane.
% 
Likewise, for the \emph{alt} structure we found that, for an energy of the
incoming beam of 1.972\,eV, the responses reach maximum values of
$|\mathcal{V}^{\mathrm{x}} (\omega,\alpha)| = 9.9$\,Km/s with spin
% polarization angles $\theta_{\mathrm{x}} (\omega,\alpha) = 129^ {\circ}$ and
% $\varphi_{\mathrm{x}} (\omega,\alpha)=229^{\circ}$ 
directed downward the third Cartesian quadrant of the $xy$ plane; and
$|\mathcal{V}^{\mathrm{y}} (\omega,\alpha)| = 49.4$\,Km/s with spin
polarization angles $\theta_{\mathrm{y}} (\omega,\alpha) = 127^{\circ}$ and
$\varphi_{\mathrm{y}} (\omega,\alpha)=227^{\circ}$ directed downward the third
Cartesian quadrant.

According to these results both structures are excellent candidates for
spintronics applications.
